Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-17 manuscript_results.Rmd
code review line 1690

Now I will combine all these plots.

@@

    # Generate histogram
    p <- ggplot(dataset, aes(x = .data[[given_model]])) +
      geom_histogram(color = "black", fill = "lightblue", bins = 30, alpha = 0.7) +
      geom_vline(aes(xintercept = mean_val), color = "red", linetype = "dashed", linewidth = 1) +
      geom_vline(aes(xintercept = mean_val - sd_val), color = "blue", linetype = "dotted", linewidth = 1) +
      geom_vline(aes(xintercept = mean_val + sd_val), color = "blue", linetype = "dotted", linewidth = 1) +
      labs(title = paste("Histogram of", var, "in", dataset_name),
           x = var, 
           y = "Frequency") +
      theme_minimal()

>>>>

Now I will combine all these plots 2x2.

@@

    # Generate histogram
    p <- ggplot(dataset, aes(x = .data[[given_model]])) +
      geom_histogram(color = "black", fill = "lightblue", bins = 30, alpha = 0.7) +
      geom_vline(aes(xintercept = mean_val), color = "red", linetype = "dashed", linewidth = 1) +
      geom_vline(aes(xintercept = mean_val - sd_val), color = "blue", linetype = "dotted", linewidth = 1) +
      geom_vline(aes(xintercept = mean_val + sd_val), color = "blue", linetype = "dotted", linewidth = 1) +
      labs(title = paste("Histogram of", given_model, "target week", target_week_),
           x = given_model, 
           y = "Frequency") +
      theme_minimal()
